Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-24 paper/paper.tex
comment
update
clarification

\hy{Need to be revised.}

@@

We call the triple part of a log \textit{trace}. This part records all the random 
choices of an execution. Thus, if the trace of a log is fixed, the rest of the log 
is decided determistically by the program. A trace induces
a sequence of pairs $(G_j, y_j)$ of distributions and values of
\textit{observed} random variables. We call this sequence an \textit{image} and
denote it by $\pmb{y}$. For notational simplicity we assume that the program
always generates the same ordered set $\pmb{z}$ of \textit{results} $z_k$.

The target density $\pi(\vec{x}) := \gamma(\vec{x}) / Z$ of a program
is defined in terms of the product of the probabilities of all random
choices $\pmb{x}$ and the likelihood of all observations $\pmb{y}$
\begin{align}
  \gamma(\pmb{x}) 
  &:= 
  \prod_{i=1}^{\left|\pmb{x}\right|}
  p_{F_i}(x_i) \prod_{j=1}^{\left|\pmb{y}\right|}p_{G_j}(y_{j}).
  \label{eqn:p-trace}
\end{align}
The objective of inference in probabilistic program $\mathcal{P}$
is to characterize the distribution of $\pmb{z}$.

>>>>

@@

We call the triple part of a log \textit{trace}, and denote this sequence of $(F,x,\alpha)$'s 
by $\pmb{x}$. This part records all the random 
choices of an execution. Thus, if the trace of a log is fixed, the rest of the log 
is decided determistically by the program. A trace $\pmb{x}$ induces
a sequence of pairs $(G_j, y_j)$ of distributions and values of
\textit{observed} random variables. We call this sequence \textit{image of $\pmb{x}$} and
denote it by $\pmb{y}$. A subset of random choices in $\pmb{x}$ forms the result of the program.
We denote this result (i.e. the subsequence of $\pmb{x}$ with these choices) by $\pmb{z}$. 
%For notational simplicity we assume that the program
%always generates the same ordered set $\pmb{z}$ of \textit{results} $z_k$.
%
%\hy{What is $\pmb{z}$? It is not explained here. I found it easier to think
%that probabilistic programs define distributions over traces. Also, $\vec{x}$ is not defined.}

The target density $\pi(\vec{x}) := \gamma(\vec{x}) / Z$ of a program
is defined in terms of the product of the probabilities of all random
choices $\pmb{x}$ and the likelihood of all observations in the image $\pmb{y}$ 
of $\pmb{x}$:
\begin{align}
  \gamma(\pmb{x}) 
  &:= 
  \prod_{i=1}^{\left|\pmb{x}\right|}
  p_{F_i}(x_i) \prod_{j=1}^{\left|\pmb{y}\right|}p_{G_j}(y_{j}).
  \label{eqn:p-trace}
\end{align}
This density induces the distribution of the results $\pmb{z}$ of the program
by marginalization. The objective of probabilistic inference 
is to characterize this distribution of $\pmb{z}$.
